---
title: "Introduction to lab5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to lab5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab5)
```

## Fetching questions

`get_questions()` downloads trivia questions from the [Open Trivia Database](https://opentdb.com). It handels the session token, decodes the base64-encoded text the API returns, and automatically splits requests for more than 50 questions into several calls to respect the API's rate limit.

```{r}
Sys.sleep(6)
qs <- get_questions(amount = 10, difficulty = "easy")
head(qs)
```

Leaving `difficulty`unset returns questions of any difficulty:

```{r}
Sys.sleep(6)
qs_mixed <- get_questions(amount = 20)
table(qs_mixed$difficulty)
```

Each question also has a `category`, a `type` (`"multiple"` or `"boolean"`), a `correct_answer`, and a list-column `incorrect_answers` with the remaining options:

```{r}
qs_mixed$category[1]
qs_mixed$incorrect_answers[[1]]
```

## Visualizing the results

`plot_questions()` shows how many questions were returned per category, split by difficulty:

```{r, fig.width = 10, fig.height = 7, out.width = "100%"}
plot_questions(qs_mixed)
```
